The Astropy Project

### 2017-10-24 main.tex
reference to Jammalamadaka & Sengupta

{\subsubsection{Circular Statistics}
A set of circular statistical estimators based on [XXX] are implemented in the \package{stats} package.  These functions provide measurements of the circular mean, variance, and moment.   For all of these functions, they work with both numpy.ndarrays (assumed to be in radians) and Quantity objects.  In addition, the package includes tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the maximum likelihood estimator for the parameters of the von Mises distribution [XXX].

>>>>

{\subsubsection{Circular Statistics}

A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in the \package{stats} package.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the package includes
tests for Raleigh Test [XXX], vtest [XXX], and a function to compute the
maximum likelihood estimator for the parameters of the von Mises distribution
[XXX].
